---
title: "Lab4A"
author: "Nicolas Ferlanti"
date: "9/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
```

```{r}
report_03_11_2020 <-   read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-11-2020.csv")) %>%
  rename(Country_Region = "Country/Region", Province_State = "Province/State")
str(report_03_11_2020)
view(report_03_11_2020)
```
```{r}
library(DT)
datatable(report_03_11_2020)
```

### Exercise 1
#### ***1**
```{r}
report_03_13_2020 <-   read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-13-2020.csv")) %>%
  rename(Country_Region = "Country/Region", Province_State = "Province/State")
str(report_03_13_2020)
view(report_03_13_2020)
```
```{r}
report_09_13_2020 <-   read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/09-13-2020.csv")) %>%
  rename(Country_Region = "Country_Region", Province_State = "Province_State")
str(report_09_13_2020)
view(report_09_13_2020)
```
#### ***2**
```{r}
report_03_13_2020 %>% 
  group_by(Country_Region) %>% 
summarize(Deaths = sum(Deaths))
```
```{r}
report_09_13_2020 %>% 
  group_by(Country_Region) %>% 
summarize(Deaths = sum(Deaths))
```
#### ***3**
```{r}
report_03_13_2020 %>% 
  filter(Country_Region == "US") %>% 
  group_by(Province_State) %>% 
  summarize(cases = sum(Confirmed))
```
```{r}
report_09_13_2020 %>% 
  filter(Country_Region == "US") %>% 
  group_by(Province_State) %>% 
  summarize(cases = sum(Confirmed))
```

#### **4**   
```{r}
top10deaths0313 <- report_03_13_2020 %>% 
  group_by(Country_Region) %>% 
  summarize(Deaths = sum(Deaths)) %>% 
  arrange(desc(Deaths)) %>% 
  slice_max(Deaths, n = (10))
top10deaths0913 <- report_09_13_2020 %>% 
  group_by(Country_Region) %>% 
  summarize(Deaths = sum(Deaths)) %>% 
  arrange(desc(Deaths)) %>% 
  slice_max(Deaths, n = (10))
```
```{r}
top10deaths0313
```
```{r}
top10deaths0913
```
### Exercise Part 2
#### **5**
```{r}
top10cases0313 <- report_03_13_2020 %>% 
  group_by(Country_Region) %>% 
  summarize(cases = sum(Confirmed)) %>% 
  arrange(desc(cases)) %>% 
  slice_max(cases, n = (10))
top10cases0913 <- report_09_13_2020 %>% 
  group_by(Country_Region) %>% 
  summarize(cases = sum(Confirmed)) %>% 
  arrange(desc(cases)) %>% 
  slice_max(cases, n = (10))
top10cases0313
top10cases0913
```
### Top 10 Countries with the Most Confirmed Cases as of 03/13/2020
```{r}
ggplot(data = top10cases0313, aes(x = Country_Region, y = cases))  +
  geom_point()
```

### Top 10 Countries with the Most Confirmed Cases as of 09/13/2020
```{r}
ggplot(data = top10cases0913, aes(x = Country_Region, y = cases))  +
  geom_point()
```

### Top 10 Countries with the Most Deaths as of 03/13/2020
```{r}
ggplot(data = top10deaths0313, aes(x = Country_Region, y = Deaths))  +
  geom_point()
```

### Top 10 Countries with the Most Deaths as of 09/13/2020
```{r}
ggplot(data = top10deaths0913, aes(x = Country_Region, y = Deaths))  +
  geom_point()
```

##### **6**
```{r}
top10casesUS0313 <- report_03_13_2020 %>% 
  filter(Country_Region == "US") %>% 
  group_by(Province_State) %>% 
  summarize(cases =sum(Confirmed)) %>% 
  arrange(desc(cases)) %>% 
  slice_max(cases, n =(10))
top10casesUS0313

top10casesUS0913 <- report_09_13_2020 %>% 
  filter(Country_Region == "US") %>% 
  group_by(Province_State) %>% 
  summarize(cases =sum(Confirmed)) %>% 
  arrange(desc(cases)) %>% 
  slice_max(cases, n =(10))
top10casesUS0913

top10deathsUS0313 <- report_03_13_2020 %>% 
  filter(Country_Region == "US") %>% 
  group_by(Province_State) %>% 
  summarize(Confirmed = sum(Confirmed), Deaths = sum(Deaths), min_deaths = min(Deaths)) %>% 
  arrange(desc(min_deaths)) %>% 
  slice(1:10)
top10deathsUS0313

top10deathsUS0913 <- report_09_13_2020 %>% 
  filter(Country_Region == "US") %>% 
  group_by(Province_State) %>% 
  summarize(Deaths = sum(Deaths)) %>% 
  arrange(desc(Deaths)) %>% 
  slice_max(Deaths, n = (10))
top10deathsUS0913
```

### Top 10 US States with Most Confirmed Cases as of 03/13/2020
```{r}
  ggplot(data = top10casesUS0313,  aes(x = cases,  y = Province_State)) + 
    geom_bar(stat = 'identity') 
```

### Top 10 US States with Most Confirmed Cases as of 09/13/2020
```{r}
  ggplot(data = top10casesUS0913,  aes(x = cases,  y = Province_State)) + 
    geom_bar(stat = 'identity') 
```

### Top 10 US States with Most Deaths as of 03/13/2020
```{r}
  ggplot(data = top10deathsUS0313,  aes(x = Deaths,  y = Province_State)) + 
    geom_bar(stat = 'identity') 
```

### Top 10 US States with Most Deaths as of 09/13/2020
```{r}
  ggplot(data = top10deathsUS0913,  aes(x = Deaths,  y = Province_State)) + 
    geom_bar(stat = 'identity') 
```











